% @Author: athul
% @Date:   2014-09-27 16:40:12
% @Last Modified by:   athul
% @Last Modified time: 2014-10-28 08:40:10

\documentclass[a4paper, 11pt]{letter}
\usepackage[top=0.5in, bottom=0.5in, left=1in, right=0.85in]{geometry}

\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\newcommand{\tab}[1]{\hspace{.2\textwidth}\rlap{#1}}
\newcommand{\pgbr}{\vspace{4pt} \\}
\newcommand{\company}{Samsung}

% Adjust margins for aesthetics
% \addtolength{\voffset}{-0.5in}
% \addtolength{\hoffset}{-0.3in}
% \addtolength{\textheight}{2cm}

\fontfamily{SansSerif}
\selectfont
\signature{Athul Vijayan} % Your name for the signature at the bottom

\address{Athul Vijayan \\
ED11B004 \\
4011, Ganga Hostel, IIT Madras \\
Chennai, India 600036\\
+919003193943\\
athulvijayan6@gmail.com} % Your address and phone number

\begin{document}
\begin{letter}{
Mr. ABC \\
Director, Human Relations \\
High paying company\\
trippy place 121212} % Name/title of the addressee

%----------------------------------------------------------------------------------------
%   LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------
\opening{\textbf{Dear Sir,}}
% What is your intent in writing this letter? What position are you applying for and how did you learn about it?
% Briefly introduce yourself, your major, and the degree anticipated. If you are aware of a specific opening, refer to it. If you are not aware of a specific position, state your area of interest. This paragraph can also be used to refer to the individual who recommended that you contact the organization, or other factors that prompted you to write. If possible, convey why you are interested in the organization and anything you know about their product or service.

I am writing to seek an internship opportunity for a duration of 6 months starting from second week of December 2014. I am fourth year undergraduate student in the Department of Engineering Design, Indian Institute of Technology, Madras. The Department of Engineering Design has a unique multidisciplinary course comprising of the fields of extensive Product Design, Electronics, Robotics, Solid Mechanics and CAD. among others. I am doing my minor in system engineering which gave me a good background in Machine Learning and data analysis.\pgbr
As a part of our course, we have to undergo an industrial internship for a duration of 5 months, to gain further expertise. The intention of this term is to work on a live project, or as a member of a team. This will be over the period, 8th December 2014 to 15th May 2015.\pgbr
% What are your qualifications? Why do you want to work for this organization? What would you enjoy doing for them? Sell yourself and be brief. Whet the employer’s appetite so that he/she will want to read your resume and schedule an interview.
% Describe highlights from your background that would be of greatest interest to the organization. Focus on skills, activities, accomplishments, and past experience you can contribute to the organization and its work. If possible, demonstrate that you know something about the organization and industry/field. Use action verbs that describe relevant skills and expertise you can contribute. Mention specific knowledge you may have such as computer applications, foreign languages, lab techniques, writing and editing capabilities. You are attempting to create a match or “notion of fit” between the employer’s hiring needs and your interests, experience, and skills.
My passion lies in creating amazing products which are realized by powerful technology. I have good exposure of embedded systems, Machine learning, Wireless networks and programming. As mentioned in resume, I have done various projects and internship in this field. I worked on Internet of things, circuit design, programming and web server during my previous internship. I have good PCB design skills also. \textit{IC\&SR}, IIT Madras gave me opportunity to do an IOT project- 'smart library shelf' under its \textit{Student Innovation Project} program. The project aimed at connecting all the books in a library to Internet and use it to track location of book.\\ I realize the huge potential of  Internet of Things and wish to work towards the bright future with \company.\pgbr
Minor specialization courses in System Enginnering inspired me to Machine Learning. It also led me to doing more work in Machine Learning. Union of programming skills and course works in Machine Learning enable me to make powerful algorithms. I have implemented face recognition, video classification, speech recognition, gesture recognition. I believe Internet of Things is vast potent when the data from it is used for Machine Learning and analytics.\pgbr
Serving over 450 inmates of my hostel as Technical Affairs Secretary, I developed leadership, team work and communication skills. \pgbr
% What is your plan of action? Do you want to follow up with a phone call or do you want them to contact you?
% Close your letter by stating that you would like to discuss employment opportunities or other information with the individual and that you will call to follow up on your letter. This demonstrates your initiative and follow-through and will help you maintain some control of your efforts.
I feel it would be amazing to work towards future in \company \ as I feel \company's works and my areas of interest has lot of parallels. As the internship is of 5 months duration, I believe I can contribute significantly towards the project.\pgbr
I look forward to hearing from you in the near future and am available for an interview at your convenience. Please contact me with any questions you may have. Thank you for your time and consideration.

Sincerely,
\vspace{2\parskip} % Extra whitespace for aesthetics
\newline

\noindent
Athul Vijayan
\end{letter}
\end{document}